---
title: "Media Attention to Political Topics"
output: html_document
---

Modeling patterns of daily changes in salience of political topics in US news websites during 2016 (Feb - Nov).

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='hide', echo=FALSE)

require(data.table)
require(DT)
require(ggplot2)
require(cowplot)
require(e1071)
require(EnvStats)
require(DescTools)

load(file = "model")
load(file = "topics")
```

```{r plot_s_irf}

plotIRF <- function(topicID, comparisons = "", h = 30){
        lapply(topicID, function(i) {
                if (comparisons == ""){
                        ir <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[1]]$model$phi, ma = ARIMA_BASIC[[i]][[1]]$model$theta, lag.max = h)))
                        plot(y = ir, x = c(1:(h+1)), type = "l", lwd = 2, main = TOPICS[[i]], ylab = "Shock", xlab = "Days", xlim = range(1,(h+1)), ylim = range(0,1)) #), sub = skewness(ir)+kurtosis(ir))
                } else if(comparisons == "states"){ 
                        black <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[1]]$model$phi, ma = ARIMA_BASIC[[i]][[1]]$model$theta, lag.max = h)))
                        blue <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[5]]$model$phi, ma = ARIMA_BASIC[[i]][[5]]$model$theta, lag.max = h)))
                        red <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[6]]$model$phi, ma = ARIMA_BASIC[[i]][[6]]$model$theta, lag.max = h)))
                        purple <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[7]]$model$phi, ma = ARIMA_BASIC[[i]][[7]]$model$theta, lag.max = h)))
                        

                        plot( y = black,x = c(1:(h+1)), type = "l", lwd = 2,  ylab = "Shock", xlab = "Days", xlim = range(1,(h+1)), ylim = range(0,1), main = TOPICS[[i]]) 
                        plot( y = blue,x = c(1:(h+1)), type = "l", lwd = 2, ylab = "Shock", xlab = "Days", xlim = range(1,(h+1)), ylim = range(0,1), col = "blue") 
                        plot( y = red, x = c(1:(h+1)), type = "l", lwd = 2, ylab = "Shock", xlab = "Days", xlim = range(1,(h+1)), ylim = range(0,1), col = "red")
                        plot( y = purple, x = c(1:(h+1)), type = "l", lwd = 2, ylab = "Shock", xlab = "Days", xlim = range(1,(h+1)), ylim = range(0,1), col = "purple")
                                                                                     
                } else if (comparisons == "sites"){
                        black <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[1]]$model$phi, ma = ARIMA_BASIC[[i]][[1]]$model$theta, lag.max = h)))
                        orange <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[3]]$model$phi, ma = ARIMA_BASIC[[i]][[3]]$model$theta, lag.max = h)))
                        green <- cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[4]]$model$phi, ma = ARIMA_BASIC[[i]][[4]]$model$theta, lag.max = h)))
                        
                        sites <- as.data.table(cbind(black, orange, green, days = c(0:h)))
                        sites <- melt(sites, id.vars = "days")
                        setnames(sites, c("Days", "Color","Shock"))
                        sites[, variable := as.factor(Color)]
                        
                        qplot(data = sites, y = Shock, x = Days, group = Color, colour = Color, main = TOPICS[[i]]) + geom_line() + scale_color_manual(values = levels(sites$Color)) + theme(legend.position='none') + scale_x_discrete(breaks = c(1:(h+1)), limits = as.character(c(1:(h+1))), labels = as.character(c(1:(h+1))))       
                }                
        })
}


```



```{r topics, results='hide'}
TOPICS
```

## All Media Sources

### Policy Issues
```{r issues_all}
par(mfrow = c(1,2))

plotIRF(25)
plotIRF(31)

plotIRF(12)
plotIRF(8)

plotIRF(18)

```

### Presidential Candidates

```{r candidates_all}
par(mfrow = c(1,2))

plotIRF(37)
plotIRF(28)

plotIRF(27)
plotIRF(29)
plotIRF(30)
```



## Compare sites by origin - Nationwide Sources vs. Local Sources

orange = nationwide sources
green - local sources

### Policy Issues: 

```{r issues_sites, include=FALSE}

a <- plotIRF(7, comparisons = "sites")
b <- plotIRF(25, comparisons = "sites")

plot_grid(a[[1]],b[[1]])

a <- plotIRF(24, comparisons = "sites")
b <- plotIRF(8, comparisons = "sites")

plot_grid(a[[1]],b[[1]])

a <- plotIRF(14, comparisons = "sites")

```


### Presidential Candidates

```{r candidates_sites, include=FALSE}

a <- plotIRF(27, comparisons = "sites")
b <- plotIRF(29, comparisons = "sites")

plot_grid(a[[1]],b[[1]])

plotIRF(30, comparisons = "sites")

```


## Compare States by Color - Local Sources only

for each topic:

black (top left) = benchmark (all sources)

blue (top right) = sources from blue states

red (bottom left) = sources from red states

purple (bottom rigth) = sources from purple states

```{r issues_states, include=FALSE}
par(mfrow = c(2,2))

plotIRF(7, comparisons = "states")
plotIRF(25, comparisons = "states")
plotIRF(13, comparisons = "states")
plotIRF(14, comparisons = "states")
plotIRF(32, comparisons = "states")

```



### Presidential Candidates
```{r candidates_states, include=FALSE}

par(mfrow = c(2,2))

plotIRF(28, comparisons = "states")
plotIRF(27, comparisons = "states")
plotIRF(29, comparisons = "states")

```

```{r skeweness, include=FALSE}
h = 6

j = 1

SKEWENESS <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(skewness(x))
        return(skewness(x, method="l.moment"))
})
```

```{r kurtosis}
h = 6

j = 1

KURTOSIS <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(kurtosis(x, method="l.moment"))
})
```

```{r area}
h = 6

j = 1

AREA <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(as.numeric(AUC(x = c(0:h), y = x), method = "spline"))
})
```

```{r smoothness}
h = 6

j = 1

IRF_SMOOTH <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        
        plot(y = x, x = c(0:h), type = "b")
        lines(smooth.spline(x = c(0:6), y = x))
})
```

```{r slope}
h = 6

j = 1

IRF_SLOPE <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(D1tr(y = x, x = c(0:h)))
})

```

```{r shape}
h = 6

j = 1

IRF_SHAPE <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(D1tr(y = D1tr(y = x, x = c(0:h)), x = c(0:h)))
})

```

```{r 1stDerivative}
h = 6

j = 1

IRF_1DERIV <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(D1ss(y = x, x = c(1:(h+1))))
})

```


```{r 2ndDerivative}
h = 6

j = 1

IRF_2DERIV <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        #return(kurtosis(x))
        return(D2ss(y = x, x = c(0:h)))
})

```


```{r hist_ir}
h = 6

j = 1

IRF_HIST <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        hist(x)
})
```

```{r variance}
h = 6

j = 1

VARIANCE <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        return(var(x))
})
```


```{r numPeaks}
h = 6

j = 1

PEAKS <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        return(length(x[which(diff(sign(diff(x)))==-2)+1])+1)
})
```

```{r numDays}
h = 6

j = 1

DAYS <- lapply(seq_along(TOPICS), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]][[j]]$model$phi, ma = ARIMA_BASIC[[i]][[j]]$model$theta, lag.max = h)))
        decay <- h+1
        while (abs((x[decay] - x[decay - 1])) < 0.01){
                decay <- decay - 1
        }
        return(decay)
})
```

```{r irf}

h = 100

IRF <- lapply(seq_along(TOPICS[interesting]), function(i){
        x = cumsum(c(1, ARMAtoMA(ar = ARIMA_BASIC[[i]]$model$phi, ma = ARIMA_BASIC[[i]]$model$theta, lag.max = h)))
})

IRF <- setNames(IRF, TOPICS[interesting])
```

```{r plotly_irf}

h = 100

pltly <- plotly::plot_ly(type = "scatter", mode = "lines") 
for (i in 1: length(TOPICS[interesting[c(1,4,6,8)]])){
        pltly <- plotly::add_trace(p = pltly, y = IRF[c(1,4,6,8)][[i]][1:h], x = c(0:(h-1)), name = TOPICS[interesting[c(1,4,6,8)]][i])
}

pltly

```

```{r plotly_ts}

pltly <- plotly::plot_ly(type = "scatter", mode = "lines") 
for (i in 1: length(TOPICS[interesting[c(1,4,6,8)]])){
        pltly <- plotly::add_trace(p = pltly, y = byTopic[interesting[c(1,4,6,8)]][i]$score, x = byTopic[interesting[c(1,4,6,8)]][i]$publish_date, name = TOPICS[interesting[c(1,4,6,8)]][i])
}

pltly

```


```{r typology}
TYPE <- c(NA, 2, NA, NA, NA, NA, NA, 1, NA, NA, NA, 1, NA, 2, NA, NA, NA, 1, 1, NA, NA, NA, 3, 2, 3, NA, 3, 3, 2, 1, 2, 3, NA, NA, NA, NA, 1)

typology <- data.table(cbind(TOPICS, DAYS, TYPE))
typology[, DAYS := as.character(DAYS)]
typology <- typology[interesting]

setorder(typology, DAYS)

typology
```

```{r texts}
###############################################################################
#                          READ TEXT PER CATEGORY                             #        
###############################################################################



# show first and last (chronologicaly) sentences from articles each category, along with category_broba
# or set key to include category_proba to examine strength at top/bottom
texts = lapply(seq_along(TOPICS), FUN = function(i){
        # datatable(rbind(
        #         head(
        #                 DT[.(CATEGORIES[i]), .(title, sent_text, category_proba), by = article_id], 
        #                 options = list(autoWidth = T)),
        #         tail(
        #                 DT[.(CATEGORIES[i]), .(title, sent_text, category_proba), by = article_id], 
        #                 options = list(autoWidth = T))))
        datatable(texts[!is.na(TOPICS[inte]), .(publish_date, site, title),], 
                  options = list(autoWidth = T))
})
```


